Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-30 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
added figures after katias suggestions and made progress on text
.

\begin{figure}
	\centering
	\includegraphics[width=0.25\linewidth]{SFig11.png}
	\caption{{\bf Schematic depicting parameters of Optimization.} This schematic shows an example optimization geometry  at a complexity level of five diagonals. For each set of even diagonals, we allow each diagonal to travel away from each other from the center junction with distances $S_1,S_2$. Note that for every odd diagonal, the distance $S_0=0$ and it is not allowed to vary in order to ensure symmetry. }
	\label{OptimizationSchematic}
\end{figure}

@@

\KB{add expression for the target function}

@@

\section{Local and Global Instabilities}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.25\linewidth]{SFig11.png}
	\caption{{\bf Schematic depicting parameters of Optimization.} This schematic shows an example optimization geometry  at a complexity level of five diagonals. For each set of even diagonals, we allow each diagonal to travel away from each other from the center junction with distances $S_1,S_2$. Note that for every odd diagonal, the distance $S_0=0$ and it is not allowed to vary in order to ensure symmetry.}
	\label{OptimizationSchematic}
\end{figure}

@@

\KB{add expression for the target function} 
\\\mf{The target function is simply 1/ buckling reaction force, should we just keep this verbally instead of mathematically?}

@@

\section{Local and Global Instabilities}
\mf{How should I go about describing this here?}
